---
title: "rm_h5se"
author: "Sean Maden"
output: html_document
---

Recount Methylation data are contained in 3 directories, `h5se_rg`, `h5_gr`, and `h5_gm`. These contain assay files with DNAm data.

In R, these are handled as objects of class `HDF5-SummarizedExperiment`, which utilizes DelayedArray. This vignette provides an example workflow compatible with the DelayedArray backend to speed up queries of large datasets, such as the  database files. 

For expediency, this uses a small test , but similar principles apply to the full dataaset objects.

# Making the test H5SE object (code not run)
First, download H5SE data, `h5se_rg_test`, `h5se_gr_test`, and `h5se_gm_test`, can be downloaded from `recount.bio/data`. 

```{r, h5se_test}
fn <- "remethdb_h5se_gr_00-00-01_1583780004"
h5se.path <- paste0(".", "recount.bio", "data", fn, collapse = "/")

library(HDF5Array)

HDF5Array::
```


# Obtain test datasets

First, H5SE test datasets, `h5se_rg_test`, `h5se_gr_test`, and `h5se_gm_test`, can be downloaded from `recount.bio/data`. 

```{r}
library(DelayedArray)


```


# Metadata queries

Next, access the metadata with `minfi::pData(h5se_rg_test)`.

# 





